Modeling Intervention Strategies for United States TB Control

### 2013-10-14 in_progress/presentations/paper/draft.tex
edited Basic Structure

\section{Methods}
\subsection{Basic Implementation}
Both the basic Hill Model and this extended Hill Model were implemented in
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The systems of differential equations used in the Basic
Hill Model and the extended Hill Model to capture basic disease dynamics are
shown below in Figure 2 and Figure 3 respectively. In the extended Hill model,
more differential equations were implemented to add additional tracking and
economic modeling. These equations are detailed in the appendix.

>>>>

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
Model) were implemented in 
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The systems of differential equations usedto capture basic disease dynamics in the Basic Hill Model and the Extended Hill Model are
shown below in Figure 2 and Figure 3 respectively. In the Extended Hill Model,
more differential equations were implemented to add additional tracking and
economic modeling. These equations are detailed in the Appendix.
